### 2015-03-18 ConferencePaper/DraftEdwardsWoods.Rnw
Added the weights to the models and working on bootstrap estimator.

OrthodoxSQFT<-lm(TOTSQFT_EN~RENTHELP+StrTenure+Income+reporttot+reporttot:EthRace+EDUCATION+UR, data=RECS)
xtable(OrthodoxSQFT,caption="Orthodox Square Foot Model",label="tab:OrthoSQFT")

@@

<<OrthodoxStructTenure,echo=FALSE,results=tex>>=

>>>>

OrthodoxSQFT<-lm(TOTSQFT_EN~RENTHELP+StrTenure+Income+reporttot+reporttot:EthRace+EDUCATION+UR, data=RECS, weights=NWEIGHT)
xtable(OrthodoxSQFT,caption="Orthodox Square Foot Model",label="tab:OrthoSQFT")

@@

<<OrthodoxStructTenure,echo=FALSE,results=verbatim>>=
# Recreating what Edwards did in Stata
#Output is not pretty  ***TODO Make Output pretty ***
# mlogit owndwel rentass totsqft_en lnincome nhsldmem reporttot i.education i.householder_race#c.reporttot urbanrural, base(1)
library(nnet)
OrthodoxStructTenure<-multinom(StrTenure~ RENTHELP+TOTSQFT_EN+Income+NHSLDMEM+ reporttot+EDUCATION+reporttot+reporttot:EthRace+UR,data=RECS,weights=NWEIGHT)
summary(OrthodoxStructTenure)
#xtable(summary(OrthodoxStructTenure),caption="Orthodox Structure and Ownership Model",label="tab:OrthoStructTenure")
@

### 2015-03-18 ResearchNotes/Notes.Rmd
Added a table and a few graphics and made the files easier to work with in different file systems.
Added the weights to the models and working on bootstrap estimator.

>>>>

# The bootstrap of the system

Start with the existing objects for the three models
 "OrthodoxKWH"          "OrthodoxSQFT"         "OrthodoxStructTenure"

 and data

First lets get only the parts of recs with complete cases for the models

```{r}
VarsUsed<-unique(c(all.vars(formula(OrthodoxKWH)),all.vars(formula(OrthodoxSQFT)),all.vars(formula(OrthodoxStructTenure)),"NWEIGHT"))
SubsetRECS<-RECS[VarsUsed]
SubsetRECS<-SubsetRECS[complete.cases(SubsetRECS),]

#copy the objects
CopyKWH<-update(OrthodoxKWH,.~.,SubsetRECS)
CopySQFT<-update(OrthodoxSQFT,.~.,SubsetRECS)
CopyTenure<-OrthodoxStructTenure

#First Round of Square foot forecast
SubsetRECS$PSQFT<-predict(update(CopySQFT,.~. ,data=SubsetRECS))

#Find tenure probabilities with new sqft estimates
update(CopyTenure,.~.-TOTSQFT_EN + PSQFT,data=SubsetRECS )
StructProb<-predict(update(CopyTenure,.~.-TOTSQFT_EN + PSQFT,data=SubsetRECS ), type="probs")

RECSTemp<-cbind(SubsetRECS,StructProb)

#Run through again for new square foot estimate
RECSTemp$PSQFT<-predict(update(CopySQFT,.~. ,data=RECSTemp))

#Alter formula in KWH model for new variables
summary(CopyKWH)
update(CopyKWH, .~ .-TOTSQFT_EN + PSQFT, data=RECSTemp)

```{r}
update(OrthodoxStructTenure)$fitted.values
all.vars(formula(OrthodoxKWH))
all.vars(formula(OrthodoxSQFT))
all.vars(formula(OrthodoxStructTenure))
